### 2022-05-30 main/chapter_2ljets.tex
begin 2ljets context

Various previous incarnations of this search have been conducted with similar
selections and target models on in older data, including partial Run~2~\cite{
atlas_susy_strong_2l_partial_run2_1,
atlas_susy_strong_2l_partial_run2,
cms_susy_2016_strong_2l_run2_1,
cms_susy_2016_strong_2l_run2
} and Run~1~\cite{
atlas_susy_strong_2l_run1,
cms_susy_2016_strong_2l_run1
} in \atlas\ and \cms.
One can cherry-pick excesses in these Run~1 searches,
of ``$3.0$ standard deviations'' in \atlas~\cite{atlas_susy_strong_2l_run1}
and ``$2.6$ standard deviations'' in \cms~\cite{cms_susy_2016_strong_2l_run1}.
These excesses were not reproduced in their early Run~2 updates.

@@

\subsection{Electroweak}
\label{sec:2ljets_origins_electroweak}
% susy motivation
% 2/3l, older 2l context
% update with run 2
% multi-bin fit
% orthogonal regions

>>>>

Various previous incarnations of this search have been conducted with similar
selections and target models on in older data, including partial Run~2~\cite{
atlas_susy_strong_2l_partial_run2_1,
atlas_susy_strong_2l_partial_run2,
cms_susy_2016_strong_2l_run2_1,
cms_susy_2016_strong_2l_run2
} and Run~1~\cite{
atlas_susy_strong_2l_run1,
cms_susy_2016_strong_2l_run1
} in \atlas\ and \cms.
From these Run~1 searches, one can cherry-pick excesses
of ``$3.0$ standard deviations'' in \atlas~\cite{atlas_susy_strong_2l_run1}
and ``$2.6$ standard deviations'' in \cms~\cite{cms_susy_2016_strong_2l_run1}.
These excesses of data above estimated backgrounds were not reproduced in their
early Run~2 updates.

@@

\subsection{Electroweak}
\label{sec:2ljets_origins_electroweak}
% susy motivation

As motivated in the previous sections, I personal tastes for how searches
should be constructed.
One taste is for simulation-driven background estimates, since they are
interpretable as representations of the Standard Model and they can exceed the
precision available in data alone.
Another is for orthogonal regions, such that their likelihoods are independent
and the information in their data can be cleanly combined.

The core idea behind the design of the $\twoljets$-electroweak analysis is to
update the regions of the partial Run~2 search~\cite{atlas_23l_SUSY_2016_24},
(its $2\ell + jets$ channel).
A particular goal was to improve sensitivity by replacing their overlapping
`SR2-Int' and `SR2-High' regions with orthogonal, combined selections.
\emph{I am grateful to Sarah Williams for suggesting this approach.}

% run1
\TODO{run 1?}
\cite{atlas_2l_SUSY_2013_11}

\TODO{CMS papers, compare exclusion}

\TODO{sr2 int high figure}

% 2/3l, older 2l context
% update with run 2
% multi-bin fit
% orthogonal regions
